%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
% \addbibresource{bibliography.bib}

\begin{document}
\header{Jeffrey }{Kwan}
       {full stack software engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    San Francisco, CA
    (415) 689-3783
    ~
    \href{mailto:jeffreyjkwan@gmail.com}{\textbf{jeffreyjkwan@}\\gmail.com}
  \section{programming\\languages}
    JavaScript
    (ES5, node.js)
    Java, CSS
    C, SQL
  \section{frameworks}
    AngularJS, Backbone.js
    React, Flux,
    Node.js, Spring
    Android
  \section{libraries}
    Bootstrap, D3, jQuery
    Karma, Mocha, Jasmine
    Grunt, Gulp, Yeoman
  \section{tools}
    Git, IntelliJ
    Sublime Text
    Vim
\end{aside}

\section{summary}

Three years of experience in full stack web development with a focus in front-end technologies. Helping my current company migrate to AngularJS. Experience in writing application framework, resuable web components, configuring tooling, build automation, unit and end to end test suite.

\section{experience}

\begin{entrylist}
  \entry
    {2012 - Now}
    {MyVest}
    {Software Engineer}
    {\begin{itemize}
    \item Lead member in building the foundation of MyVest’s new user interface with AngularJS. Included integrating with legacy Flex and JSP applications.
    \item Designed and built JavaScript quality automation suite. Suite includes documentation generation linting, code coverage and unit-test runner using Grunt, Karma and Jasmine.
    \item Customized the AngularJS Yeoman generator to fit company standards and structure.
    \item Built various reusable AngularJS components, including data visualization using D3 and search suggestion using Elastic Search.
    \item Designed and developed front-end applications using Backbone.js and Adobe Flex.
    \item Technical Lead and Project Manager on multiple projects. Responsibilities included gathering requirements, delegating tasks to other engineers and creating project and test plans.
    \item Mentored and trained other employees on JavaScript, AngularJS, Jasmine and Unit Testing.
    \item 2013 Engineer of the Year award winner
    \end{itemize}
    }
  \entry
    {2011}
    {Agilent Technologies}
    {Hardware Engineer Intern}
    {\begin{itemize}
    \item Developed new features and test automation for a hardware verification system.
    \item Debugged intermittent bugs and compatibility issues in various test systems.
    \item Developed a Xilinx serial bit transfer program for Windows-based systems to transfer FPGA files.
    \end{itemize}
    }
  \entry
    {2010}
    {Cisco Systems}
    {Co-op Software Engineer}
    {\begin{itemize}
    \item Assisted in the development of an application for the Cisco IOS operating system.
    \item Created multiple patches and bug fixes throughout the Cisco IOS operating system.
    \item Participated in software and test design specifications.
    \end{itemize}
    }
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2012}
    {Bachelor of Science {\normalfont in Computer Engineering}}
    {}
    {\emph{California Polytechnic State University, San Luis Obispo}}
\end{entrylist}

% \section{projects}

% \begin{entrylist}
%   \entry
%     {2012}
%     {Who did I forget ?}
%     {\href{http://whodidiforget.com}{whodidiforget.com}}
%     {Guest list recommendation for Facebook events based on friends already attending the event.}
%   \entry
%     {2011}
%     {Fellows}
%     {\href{http://fellows-exp.com}{fellows-exp.com}}
%     {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
%   \entry
%     {2008}
%     {Happy Flu}
%     {\href{http://happyflu.com}{happyflu.com}}
%     {Experiment aimed to measure viral spreading of content across the blogosphere.}
% \end{entrylist}

% \section{publications}


% \printbibsection{article}{article in peer-reviewed journal}
% \begin{refsection}
%   \nocite{*}
%   \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
% \end{refsection}
% \begin{refsection}
%   \nocite{*}
%   \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
% \end{refsection}
% \printbibsection{misc}{other publications}
% \printbibsection{report}{research reports}

\end{document}
